
%---------------------------------------%
% Packages arranged by : Tsz Timmy Chan %
%                 Date : May 26th, 2019 % 
%---------------------------------------%

\documentclass{TC}
\usepackage{TCcommon}

\title{TITLE HERE}	% Work Title Here.
\author{Tsz Timmy Chan}	% YOUR NAME HERE 

\usepackage[notes]{TCheader}
\usepackage{TCexamtitle}

\usepackage{setspace}
\linespread{1.5}

%\renewcommand{\benediction}{" " - }
%\renewcommand{\quoteoftheday}{" " \\ - }

\begin{document}
DHD 510: Research Questions

What makes good \emph{research} questions?
\begin{itemize}
\item Answerable
\item Significant (statistically)
\item Relevant to the disability community
\end{itemize}


Commitments:
\begin{itemize}
\item reflecting views \& experiences of those who are on the receiving end of policy \& practice

\item implication for to change

\item anti-ablist, anti-racist and anti-sexist
\end{itemize}

\gls{FINER}\parencite{cummings_conceiving_2007}
\begin{multicols}{2}
\begin{enumerate}
\item Feasible
	\begin{itemize}
	\item \# of participants
	\item technical expertise
	\item affordable (time \& \$\$)
	\item Manageable in scope 
	\end{itemize}
\item Interesting
	\begin{itemize}
	\item Investigator
	\item Peers
	\item Community
	\end{itemize}
\item Novel: Confirms/refutes or extends current research
\item Ethical: Make sure that study is amendable to review boards.
\item Relevant to
	\begin{itemize}
	\item scientific knowledge
	\item policy, practice and the real world
	\item future research
	\end{itemize}
\end{enumerate}
\end{multicols}

\gls{PICOT} \parencite{riva_what_2012}
\begin{enumerate}
\item Population: What specific population are you interested in learning about?
\item Investigation: What is your investigation? What will you be doing? Will you be surveying, observing, using video diaries? (Indicates methodologies)
\item Comparison Group: What is the main alternative group in contrast with the research population? (Some might not have one, if so you need to explain why.)

\item Outcome of Interest: What do you intend to accomplish, measure, improve or affect?
\item Time: What is the time-span that you will be looking at for your research? 
\end{enumerate}

\end{document}
